Provisional Title

### 2021-05-04 draft/draft.tex
figure 2 initialized, changes to analyzeData.R for smoother streamlining of plots

The sequencing protocol was identical to that described in \cite{Goldford2018}.
Community samples were collected by spinning down at 3500rpm for 25min
in a bench-top centrifuge at room temperature;
cell pellets were stored at $-80^\circ$C before processing.
To maximize Gram-positive bacteria cell wall lysis,
the cell pellets were re-suspended and incubated at $37^\circ$C for 30min
in enzymatic lysis buffer (20mM Tris-HCl, 2mM sodium EDTA, 1.2\% Triton X-100)
and 20mg/mL of lysozyme from chicken egg white (Sigma-Aldrich).
After cell lysis, the DNA extraction and purification was performed using the
DNeasy 96 protocol for animal tissues (Qiagen).
The clean DNA in $100\upmu$L elution buffer of 10mM Tris-HCl, 0.5mM EDTA
at pH 9.0 was quantified using Quan-iT PicoGreen dsDNA Assay Kit
(Molecular Probes, Inc.)
and normalized to 5ng/$\upmu$L in nuclease-free water (Qiagen)
for subsequent 16S rRNA illumina sequencing.
16S rRNA amplicon library preparation was performed following a dual-index
paired-end approach \cite{Kozich2013}.
Briefly, PCR amplicon libraries of V4 regions of the 16S rRNA were prepared 
sing dual-index primers (F515/R805), then pooled and sequenced
using the Illumina MiSeq chemistry and platform.
Each sample went through a 30-cycle PCR in duplicate of $20\upmu$L
reaction volumes using 5ng of DNA each, dual index primers, and AccuPrime Pfx SuperMix (Invitrogen).
The thermocycling procedure includes a 2min initial denaturation step at
$95^\circ$C, and 30 cycles of the following PCR scheme:
(a) 20 second denaturation at $95^\circ$C,
(b) 15 second annealing at $55^\circ$C,
and (c) 5 minute extension at $72^\circ$C.
The duplicate PCR products of each sample were pooled, purified, and normalized
using SequalPrep PCR cleanup and normalization kit (Invitrogen).
Barcoded amplicon libraries were then pooled and sequenced using
Illumina Miseq v2 reagent kit, which generated 2$\times$250bp paired-end reads
at the Yale Center for Genome Analysis (YCGA).
The sequencing reads were demultiplexed on QIIME 1.9.0 \cite{Caporaso2010}.
The barcodes, indexes, and primers were removed from raw reads,
producing FASTQ files with both the forward and reverse reads for each sample,
ready for DADA2 analysis \cite{Callahan2017}.
DADA2 version 1.1.6 was used to infer unique biological exact sequence variants
(ESVs) for each sample
and na{\"i}ve Bayes was used to assign taxonomy using the SILVA version 123
database \cite{Wang2007,Quast2013}.

>>>>

The sequencing protocol was identical to that described in \cite{Goldford2018}.
Community samples were collected by spinning down at 3500rpm for 25min
in a bench-top centrifuge at room temperature;
cell pellets were stored at $-80^\circ$C before processing.
To maximize Gram-positive bacteria cell wall lysis,
the cell pellets were re-suspended and incubated at $37^\circ$C for 30min
in enzymatic lysis buffer (20mM Tris-HCl, 2mM sodium EDTA, 1.2\% Triton X-100)
and 20mg/mL of lysozyme from chicken egg white (Sigma-Aldrich).
After cell lysis, the DNA extraction and purification was performed using the
DNeasy 96 protocol for animal tissues (Qiagen).
The clean DNA in $100\upmu$L elution buffer of 10mM Tris-HCl, 0.5mM EDTA
at pH 9.0 was quantified using Quan-iT PicoGreen dsDNA Assay Kit
(Molecular Probes, Inc.)
and normalized to 5ng/$\upmu$L in nuclease-free water (Qiagen)
for subsequent 16S rRNA illumina sequencing.
16S rRNA amplicon library preparation was performed following a dual-index
paired-end approach \cite{Kozich2013}.
Briefly, PCR amplicon libraries of V4 regions of the 16S rRNA were prepared 
sing dual-index primers (F515/R805), then pooled and sequenced
using the Illumina MiSeq chemistry and platform.
Each sample went through a 30-cycle PCR in duplicate of $20\upmu$L
reaction volumes using 5ng of DNA each, dual index primers, and AccuPrime Pfx SuperMix (Invitrogen).
The thermocycling procedure includes a 2min initial denaturation step at
$95^\circ$C, and 30 cycles of the following PCR scheme:
(a) 20-second denaturation at $95^\circ$C,
(b) 15-second annealing at $55^\circ$C,
and (c) 5-minute extension at $72^\circ$C.
The duplicate PCR products of each sample were pooled, purified, and normalized
using SequalPrep PCR cleanup and normalization kit (Invitrogen).
Barcoded amplicon libraries were then pooled and sequenced using
Illumina Miseq v2 reagent kit, which generated 2$\times$250bp paired-end reads
at the Yale Center for Genome Analysis (YCGA).
The sequencing reads were demultiplexed on QIIME 1.9.0 \cite{Caporaso2010}.
The barcodes, indexes, and primers were removed from raw reads,
producing FASTQ files with both the forward and reverse reads for each sample,
ready for DADA2 analysis \cite{Callahan2017}.
DADA2 version 1.1.6 was used to infer unique biological exact sequence variants
(ESVs) for each sample
and na{\"i}ve Bayes was used to assign taxonomy using the SILVA version 123
database \cite{Wang2007,Quast2013}.
